---
title: "Using pipfun::setup_working_release()"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using pipfun::setup_working_release()}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Intro

In the new pipeline framework, we can't work in isolation. There are many moving parts and versions, so we always need to work with a reference version. This reference version is what we call the "working release." It is termed "release" because, at the production level, we refer to release versions. It is termed "working" because it is the release version we are currently working on. The "working release" does not need to be an official PIP release; it could be a testing release. However, we must always work within a working release framework.

In this vignette, we explore how to use the `pipfun::setup_working_release()` function to set up a working release in any package.

# Setup working release

```{r setup}
# devtools::load_all(".")
library(piptest)
```

Setting up a working release is the job of the `{pipfun}` package, specifically through the `pipfun::setup_working_release()` function. This function configures an environment where the working release and other necessary variables are available for use.

In `{piptest}`, we fully import `{pipfun}` by listing `{pipfun}` in the Imports section of `{piptest}`’s DESCRIPTION file and adding `import(pipfun)` to `{piptest}`’s NAMESPACE file. This can be done in the `piptest-package.R` file, which is automatically created when you use `usethis::use_package_doc()`.

Once you load `{piptest}`, you can access all the functions in `{pipfun}`, including `pipfun::setup_working_release()`.

Working with a release means that you need to inform your R session which release you are working with. Once set, any function from any package in the PIP ecosystem should be configured to work with that release because all the packages should utilize the environment created by `pipfun::setup_working_release()`. You can set the release version by providing a date in the format "%Y%m%d" to the `release` argument. If the date exists, it will be set up. If it does not, `setup_working_release()` will throw an error, indicating that you need to create the release.


```{r setup-release-error, error=TRUE}
release <- "20250127"
pipfun::setup_working_release(release = release)
```

```{r gitcreds}
creds <- pipfun::get_github_creds()
creds
```


By default, `{pipfun}` will create a new release in the official working directory, provided you have the necessary permissions. While creating new directories is generally straightforward, deleting them can be more problematic. Therefore, the `pipfun::remove_pip_release()` function requires you to specify the directory from which you want to delete the release. This precaution helps prevent accidental deletion of important directories.

For the purpose of this vignette, let's set a temporary directory to work with. This will ensure that any changes we make are isolated and do not affect the official working directory.

For the purpose of this vignette, we will create a new  "TEST" release. 
```{r setup-release}
release <- "20250127"
temp_dir <- fs::path(tempdir(), "piptest") |> 
  fs::dir_create(recurse = TRUE)
new_release <- pipfun::new_pip_release(release = release,
                                       identity = "TEST",
                                       working_dir = temp_dir)
pipfun::setup_working_release(release = release, 
                              identity = "TEST")
```

## The `.pipenv` environment

The `pipfun::setup_working_release()` function creates a `.pipenv` environment in the empty environment. This environment contains the release version and other necessary variables. `{pipfun}` provides a set of functions to interact with the `.pipenv` environment.

```{r pipenv}
# Retrieve the entire environment
env <- pipfun::get_pipenv()
ls(env)  # List stored keys in .pipenv

# Set a variable in the environment
pipfun::set_in_pipenv("my_var", 123)

pipfun::get_from_pipenv("my_var")  # Returns 123

pipfun::get_from_pipenv("non_existent")  # Returns NULL instead of error
```


## Deleting a release

you can delete a release by using the `pipfun::pipfun::remove_pip_release()` function. This function deletes the release and the `.pipenv` environment.

```{r delete-release}
pipfun::remove_pip_release(release = release, 
                           identity = "TEST",
                           working_dir = temp_dir)
```


# package functions that make use of `.pipenv`

Once the `pipfun::setup_working_release()` has been used and a release version is set in place to work with in your package, you can interact with the `.pipenv` environment in your package functions in different ways. 

The first thing to do is to the get the release version in your functions. 

```{r get-setup-release}
wrk_release <- pipfun::get_from_pipenv("working_release")
wrk_release
```

Now, you can call the working release in any function of your package, as we are doing here with `piptest::hello()` .

You only need to do something like this:

```{r , eval=FALSE}
hello <- function() {
  pipfun::get_wrk_release()
  invisible(wrk_release)
}
```


And when you call `hell()` you'll be workinf already with the working release. 
```{r call-hello}
hello() |> 
  print()
```



